---
title: "Grass"
author: "WangJY"
date: "2022-11-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message=FALSE)
rm(list=ls())
gc()
# setwd("~/Desktop/phD/AFEC-X/GrassGang")
```

## C3/C4 matching
```{r}
library(readxl)
library(stringr)
library(tidyverse)
genuslevel <- read_xls("~/Desktop/phD/AFEC-X/GrassGang/data/genus-level.xls",sheet=1)[-c(1:6),]
colnames(genuslevel) <- genuslevel[1,]
genuslevel <- genuslevel[-1,]
genuslevel$genus <- str_split_fixed(genuslevel$`Genus Authority`,pattern=" ",n=2)[,1]
genuslevel <- genuslevel[,c("genus","Photosynthetic types")]

specieslevel <- read_xls("~/Desktop/phD/AFEC-X/GrassGang/data/species-level.xls",sheet=1)[-c(1:2),]
colnames(specieslevel) <- specieslevel[1,]
specieslevel <- specieslevel[-1,]
specieslevel <- specieslevel[,c("Species","Pathway")]
```

Now I have cleaned up dataset for C3 and C4 plant list, on genus level and species level. See below:
```{r}
head(genuslevel)
head(specieslevel)
```

```{r}
arid <- read.csv("~/Desktop/phD/AFEC-X/GrassGang/data/poaceae_mean_aridity.csv")
any(specieslevel$Species %in% arid$Species)

unique(genuslevel$`Photosynthetic types`)
genuslevel$`Photosynthetic types`[genuslevel$`Photosynthetic types`!="C3"&genuslevel$`Photosynthetic types`!="C4"&genuslevel$`Photosynthetic types`!="unknown"] <- "both"

unique(specieslevel$Pathway)
specieslevel$Pathway[specieslevel$Pathway=="C3-C4?"]<- "both"


head(arid)

GrassDataset<-arid %>% mutate(Species_old=Species,aridity.ch,count=x1,authors_WCVP,rank,accepted_name,accepted_authors,accepted_genus,accepted_family,accepted_order) %>%
  filter(!is.na(aridity.ch)) %>%
  dplyr::select(Species_old,aridity.ch,count,authors_WCVP,rank,accepted_name,accepted_authors,accepted_genus,accepted_family,accepted_order)
summary(GrassDataset$aridity.ch)

colnames(genuslevel)[1] <- c("accepted_genus")
GrassDataset <- left_join(GrassDataset,genuslevel)
unique(GrassDataset$`Photosynthetic types`)

colnames(specieslevel)[1] <- "Species_old"
GrassDataset <- left_join(GrassDataset,specieslevel)
GrassDataset[!is.na(GrassDataset$Pathway),"Photosynthetic types"] <- GrassDataset[!is.na(GrassDataset$Pathway),"Pathway"]
GrassDataset <- GrassDataset[,c(1:11)]
# write.csv(GrassDataset,"data/GrassDataset.csv",row.names=F)
```

Now I have complete dataset for Poaceae grass, with photosynthetic pathways.

## Cellulose against aridity index

```{r}
library(data.table)
library(openxlsx)
cellulose <- read_xlsx("~/Desktop/phD/AFEC-X/GrassGang/data/Lee2018_Article_AGlobalComparisonOfTheNutritiv SUPPLEMENTARY.xlsx",sheet=2)
cellulose <- cellulose[-c(1:4),1:12]
colnames(cellulose)<-cellulose[1,]
cellulose <- cellulose[-1,]

tmp <- GrassDataset[,c("Species_old","aridity.ch","accepted_name")]
colnames(tmp)[1:2] <- c("Species" ,"arid1")
cellulose <- left_join(cellulose,tmp[,c(1:2)])
tmp <- GrassDataset[,c("Species_old","aridity.ch","accepted_name")]
colnames(tmp)[2:3] <- c("arid2","Species" )
cellulose <- left_join(cellulose,tmp[,c(2:3)])

cellulose[is.na(cellulose$arid2)&!is.na(cellulose$arid1),"arid2"]<-cellulose[is.na(cellulose$arid2)&!is.na(cellulose$arid1),"arid1"]

cellulose <- cellulose[,c(1,7:12,14)]
summary(cellulose)
cellulose$ADF<- as.numeric(cellulose$ADF)
cellulose$ADL<- as.numeric(cellulose$ADL)
cellulose$Ash<- as.numeric(cellulose$Ash)
cellulose$CP<- as.numeric(cellulose$CP)
cellulose$DM<- as.numeric(cellulose$DM)
cellulose$NDF<- as.numeric(cellulose$NDF)

cellulose <- cellulose[!is.na(cellulose$NDF)&!is.na(cellulose$arid2),]
summary(cellulose)
cellulose$Species <- as.factor(cellulose$Species)
meanna <- function(vector){
  return(mean(vector,na.rm=T))
}
cell_agg <- aggregate(cellulose, by=list(cellulose$Species),FUN=mean)
cell_agg <- cell_agg[,-2]
colnames(cell_agg)[1]<- "Species"

tmp <- GrassDataset[,c("Species_old","Photosynthetic types","accepted_name")]
colnames(tmp)[1:2] <- c("Species","Pathway1")
cell_comp <- unique(left_join(cell_agg,tmp[1:2]))

tmp <- GrassDataset[,c("Species_old","Photosynthetic types","accepted_name")]
colnames(tmp)[2:3] <- c("Pathway2","Species")
cell_comp <- unique(left_join(cell_comp,tmp[2:3]))

#all same
cell_comp <- cell_comp[,-10]
hist(sqrt(cell_comp$arid2))
cell_comp$arid2.sqrt <- sqrt(cell_comp$arid2)
hist((cell_comp$NDF))





cell_supp<-read.xlsx("/Users/lilywang/Desktop/phD/AFEC-X/GrassGang/data/Grass cellulose.xlsx",sheet=1)
unique(cell_supp[,1])
cell_supp[cell_supp$Name=="Cenchrus ciliaris ",1]<-"Cenchrus ciliaris"
cell_supp[cell_supp$Name=="Cynodon dactylon ",1]<-"Cynodon dactylon"
cell_supp[cell_supp$Name=="Dichanthium annulatum ",1]<-"Dichanthium annulatum"
cell_supp[cell_supp$Name=="Panicum coloratum ",1]<-"Panicum coloratum"
cell_supp_agg<-aggregate(cell_supp,by=list(cell_supp$Name),FUN=meanna)
cell_supp_agg<-cell_supp_agg[,-2]
tmp <- GrassDataset[,c("Species_old","aridity.ch","accepted_name","count","Photosynthetic types")]
colnames(tmp)[1]<-"Group.1"
cell_supp_agg <- left_join(cell_supp_agg,tmp[,c(1,2,4,5)])
colnames(cell_supp_agg)[7]<- "Pathway1"

tmp <- GrassDataset[,c("Species_old","aridity.ch","accepted_name","count","Photosynthetic types")]
colnames(tmp)[3]<-"Group.1"
cell_supp_agg <- left_join(cell_supp_agg,tmp[,c(2,3,4,5)])

cell_supp_agg$arid.sqrt<-sqrt(cell_supp_agg$aridity.ch)
hist(cell_supp_agg$Cellulose)


cell_supp_agg%>%filter(!is.na(Pathway1))%>%ggplot()+aes(x=arid.sqrt,y=NDF,colour=Pathway1)+geom_point()+geom_smooth(method="lm")
cell_supp_agg%>%filter(!is.na(Pathway1))%>%ggplot()+aes(x=arid.sqrt,y=Cellulose,colour=Pathway1)+geom_point()+geom_smooth(method="lm")
cell_supp_agg%>%filter(!is.na(Pathway1))%>%ggplot()+aes(x=arid.sqrt,y=Hemicellulose,colour=Pathway1)+geom_point()+geom_smooth(method="lm")

 
  
cell_comp %>% filter(Pathway1=="C3"|Pathway1=="both")%>%ggplot()+aes(x=arid2.sqrt,y=NDF)+geom_point()+geom_smooth(method="lm")


cell_comp%>%filter(Pathway1!="both")%>%ggplot()+aes(x=arid2.sqrt,y=ADF-ADL,colour=Pathway1)+geom_point()+geom_smooth(method="lm")+ylab("Cellulose")




any(cell_supp_agg$Group.1%in%cell_comp[,"Species"])
cell_supp_agg<-unique(cell_supp_agg)

cell_new <- cell_supp_agg[!cell_supp_agg$Group.1%in%cell_comp[,"Species"],]
cell_exist <- cell_supp_agg[cell_supp_agg$Group.1%in%cell_comp[,"Species"],]

cell_append <- data.frame(Species=c(cell_comp$Species,cell_new$Group.1),NDF=c(cell_comp$NDF,cell_new$NDF),Cellulose=c(cell_comp$ADF-cell_comp$ADL,cell_new$Cellulose),Pathway=c(cell_comp$Pathway1,cell_new$Pathway1),arid.sqrt=c(cell_comp$arid2.sqrt,cell_new$arid.sqrt))

cell_append<-unique(cell_append)


for(i in 1:nrow(cell_append)){
  if(cell_append$Species[i]%in%cell_exist$Group.1){
    if(is.na(cell_append$Cellulose[i])){
      cell_append$Cellulose[i]<-cell_exist[cell_exist$Group.1==cell_append$Species[i],"Cellulose"]
    }
  }
}
cell_append[cell_append$Species=="Aristida longiseta ","Species"]<-"Aristida purpurea"
cell_append[cell_append$Species=="Digitaria insulares","Species"]<-"Digitaria insularis"
for(i in 1:nrow(cell_append)){
  if(cell_append$Species[i]%in%GrassDataset$Species_old){
    if(is.na(cell_append$arid.sqrt[i])){
      cell_append$arid.sqrt[i]<-sqrt(GrassDataset[GrassDataset$Species_old==cell_append$Species[i],"aridity.ch"])
    }
  }
}



hist(log(cell_append$Cellulose))
cell_append$log.Cellulose<-log(cell_append$Cellulose)

cell_append%>%filter(!is.na(Pathway)&Pathway!="both")%>%ggplot()+aes(x=arid.sqrt,y=NDF,colour=Pathway)+geom_point()+geom_smooth(method="lm")
cell_append%>%filter(!is.na(Pathway)&Pathway!="both")%>%ggplot()+aes(x=arid.sqrt,y=log.Cellulose,colour=Pathway)+geom_point()+geom_smooth(method="lm")




cell_append2 <- cell_append[!is.na(cell_append$Pathway)&cell_append$Pathway!="both",]
cell_append2$Pathway <- as.factor(cell_append2$Pathway)
summary(lm(Cellulose~arid.sqrt*Pathway, data=cell_append2))


```


Not pattern we suggested, Now I will try leaf trait

#Leaf trait

## leaf area, SLA, LDMC and leafN
```{r}
trait <- read.csv("/Users/lilywang/Desktop/phD/AFEC-X/GrassGang/data/TRY_traitdata_poales.csv")
head(trait)
colnames(trait)[1]<-"Species_old"

grasstrait <- left_join(GrassDataset,trait[,1:5])
head(grasstrait)

grasstrait$arid.sqrt <- sqrt(grasstrait$aridity.ch)
str(grasstrait)
head(grasstrait)
grasstrait <- grasstrait[grasstrait$count>=10,]
p1<-ggplot(grasstrait,aes(x=arid.sqrt,y=logSLA))+geom_point()+geom_smooth(method="lm");
p2<-ggplot(grasstrait,aes(x=arid.sqrt,y=LDMC))+geom_point()+geom_smooth(method="lm");
p3<-ggplot(grasstrait,aes(x=arid.sqrt,y=logLArea))+geom_point()+geom_smooth(method="lm");
p4<-ggplot(grasstrait,aes(x=arid.sqrt,y=leafN.sqrt))+geom_point()+geom_smooth(method="lm")
library(patchwork)
p1+p2+p3+p4
summary(lm(logLArea~arid.sqrt, data=grasstrait))
```

##Now try leaf thickness

```{r}
library(data.table)
pth <- fread("/Users/lilywang/Desktop/phD/AFEC-X/GrassGang/data/leaf_thickness_w poaceae/23473.txt")
allth <- fread("/Users/lilywang/Desktop/phD/AFEC-X/GrassGang/data/leaf_thickness/23472.txt")
head(allth)

pthf<-allth %>% filter(AccSpeciesName%in%GrassDataset$accepted_name)
rm(allth)
gc()
head(pthf)
pthf <-pthf %>% filter(!is.na(TraitID))
# write.csv(pthf,"/Users/lilywang/Desktop/phD/AFEC-X/GrassGang/data/poaceae_leafthickness.csv",row.names=F)
# pthf <- read.csv("/Users/lilywang/Desktop/phD/AFEC-X/GrassGang/data/poaceae_leafthickness.csv")
head(pthf)
pthf <- pthf[,c("AccSpeciesName","StdValue")]
colnames(pthf)[1]<-"accepted_name"
pthf <- aggregate(pthf,by=list(pthf$accepted_name),FUN=meanna)
pthf <- pthf[,-2]
pthf  <- pthf %>% filter(!is.nan(StdValue))
colnames(pthf)[1]<-"accepted_name"
thick <- left_join(GrassDataset,pthf)
thick$arid.sqrt <- sqrt(thick$aridity.ch)
hist(log(thick$StdValue))
thick$thick.log <- log(thick$StdValue)
thick %>% filter(count>=10&!is.na(thick.log))%>%ggplot()+aes(x=arid.sqrt,y=thick.log)+geom_point()+geom_smooth(method="lm")

```

##Now try leaf length
```{r}
leaf_length <- fread("~/Desktop/phD/AFEC-X/GrassGang/data/leaf_length/23622.txt")
head(leaf_length,n=10)
leaflen <- leaf_length %>% filter(DataName=="Leaf length",AccSpeciesName%in%GrassDataset$accepted_name)
rm(leaf_length)
gc()

leaflen <- leaflen %>% dplyr::select(AccSpeciesName,OrigValueStr,OrigUnitStr) %>% mutate(Value = as.numeric(OrigValueStr)) %>% dplyr::select(AccSpeciesName,Value,OrigUnitStr)

head(leaflen)
leaflen[leaflen$OrigUnitStr=="cm","Value"]<-leaflen[leaflen$OrigUnitStr=="cm","Value"]*10

leaflen <- leaflen[,-3]
summary(leaflen)
colnames(leaflen)[1]<-"accepted_name"
leaflen <- left_join(leaflen,GrassDataset[,c("accepted_name","aridity.ch","Photosynthetic.types")])
leaflen <- aggregate(leaflen,.~accepted_name+Photosynthetic.types,mean)
leaflen$arid.sqrt <- sqrt(leaflen$aridity.ch)
hist(leaflen$Value)
leaflen$log.length<-log(leaflen$Value)
hist(leaflen$log.length)

leaflen %>% filter(Photosynthetic.types!="both"&Photosynthetic.types!="unknown") %>% ggplot()+aes(x=arid.sqrt,y=log.length,color=Photosynthetic.types)+geom_point(alpha=0.2)+geom_smooth(method="lm")

# write.csv(leaflen,"~/Desktop/phD/AFEC-X/GrassGang/data/GrassLeafLength.csv",row.names=F)
```

##Now try leaf toughness
```{r}
tough <- fread("~/Desktop/phD/AFEC-X/GrassGang/data/leaf texture_sclerophylly_physical strength_ toughness/23646.txt")
head(tough)
tough$OriglName<-as.factor(tough$OriglName)
leaftgh <- tough %>% filter(OriglName=="LeafToughness",AccSpeciesName%in%GrassDataset$accepted_name) %>% dplyr::select(AccSpeciesName,OrigValueStr,OrigUnitStr)
head(leaftgh)

leaftgh <- leaftgh %>% dplyr::select(AccSpeciesName,OrigValueStr) %>%mutate(Value=as.numeric(OrigValueStr)) %>% dplyr::select(AccSpeciesName,Value)%>% aggregate(.~AccSpeciesName,mean)
colnames(leaftgh)[1]<-"accepted_name"
leaftgh <- left_join(leaftgh,GrassDataset[,c("accepted_name","aridity.ch","Photosynthetic.types")])
leaftgh <- aggregate(leaftgh,.~accepted_name+Photosynthetic.types,mean)
leaftgh$arid.sqrt <- sqrt(leaftgh$aridity.ch)


leaftgh%>%filter(Photosynthetic.types!="both"&Photosynthetic.types!="unknown") %>% ggplot()+aes(x=arid.sqrt,y=Value,color=Photosynthetic.types)+geom_point(alpha=1)+geom_smooth(method="lm")+ylab("Toughness")
```

## Leaf toughness data we collected
```{r}
coltgh <- read_xlsx("~/Desktop/phD/AFEC-X/GrassGang/data/Toughness data.xlsx",sheet=1)
head(coltgh)
coltgh <- coltgh %>% dplyr::select(Species,Mean) %>% filter(Species!="Unknown")

xtbg <- read.csv("~/Desktop/phD/AFEC-X/GrassGang/data/GrassInXTBG.csv")
colnames(coltgh)[1]<-"Binomial"
coltgh <- left_join(coltgh,xtbg[,c("Binomial","aridity.index")])
summary(coltgh)

for(i in 1:nrow(coltgh)){
  if(is.na(coltgh$aridity.index[i])){
    if(coltgh$Binomial[i]%in%GrassDataset$Species_old){
      coltgh[i,"aridity.index"] <- GrassDataset[GrassDataset$Species_old==coltgh$Binomial[i],"aridity.ch"]
    }
  }
}
coltgh[12,3]<-1.286243
coltgh[39,3]<-0.6402801

coltgh_agg <- aggregate(coltgh,Mean~Binomial+aridity.index,FUN=mean)
coltgh_agg$arid.sqrt <- sqrt(coltgh_agg$aridity.index)
hist(log(coltgh_agg$Mean))
coltgh_agg$log.tough <- log(coltgh_agg$Mean)
coltgh_agg %>% filter(log.tough<=2.4&log.tough>=0.8)%>%ggplot()+aes(x=arid.sqrt,y=log.tough)+geom_point()+geom_smooth(method="lm")
summary(lm(log.tough~arid.sqrt,data=coltgh_agg[coltgh_agg$log.tough<=2.4&coltgh_agg$log.tough>=0.8,]))



head(leaftgh)
coltgh_append <- data.frame(accepted_name=c(coltgh_agg$Binomial,leaftgh$accepted_name),arid.sqrt=c(coltgh_agg$arid.sqrt,leaftgh$arid.sqrt),Toughness=c(coltgh_agg$Mean,leaftgh$Value))

coltgh_append$log.tough <- log(coltgh_append$Toughness)
coltgh_append %>% ggplot()+aes(x=arid.sqrt,y=log.tough)+geom_point()+geom_smooth(method="lm")


coltgh_append <- left_join(coltgh_append,GrassDataset[,c("accepted_name","Photosynthetic.types")])
coltgh_append <- aggregate(coltgh_append,.~accepted_name+Photosynthetic.types,FUN=mean)
coltgh_append %>% ggplot()+aes(x=arid.sqrt,y=log.tough,color=Photosynthetic.types)+geom_point()+geom_smooth(method="lm")

summary(lm(log.tough~arid.sqrt*Photosynthetic.types,data=coltgh_append))


xtbg_now<-xtbg[,c(1,2,5)]
xtbg_now <- left_join(xtbg_now,coltgh_agg[,c(1,3)])
```
##Grass distribution data
```{r, eval=FALSE}
grassdistri <- fread("~/Desktop/phD/AFEC-X/GrassGang/data/BIEN_poaceae.csv")
head(grassdistri)
length(unique(grassdistri$Species))
plot(grassdistri[,c("longmid","latmid")])
summary((grassdistri %>% count(Species))$n)
library(rgdal)
coordinates(grassdistri)<-c("longmid","latmid")
proj4string(grassdistri) <- CRS('+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs')
mollweide <- "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84"

library(raster)
airas <- raster("~/Desktop/phD/AFEC-X/GrassGang/data/Aridity/ai_v3_yr.tif")
plot(airas)
crs(airas) #WGS1984
res(airas) # 0.0083333
airas_agg <- aggregate(airas, fact=60, fun=mean)
# writeRaster(airas_agg,"~/Desktop/phD/AFEC-X/GrassGang/data/Aridity/aridity_0.5deg.tif")
rm(airas)
gc()

res(airas_agg)
summary(values(airas_agg))
values(airas_agg) <- values(airas_agg)*0.0001
plot(airas_agg)
Global_Cell <- as.data.frame(rasterToPoints(airas_agg))
Global_Cell$ID=1:length(values(airas_agg))
Global_Cell$AI <- extract(airas_agg,Global_Cell[,c("x","y")],method="simple")

Global_Cell <- Global_Cell[,c("ID","x","y","AI")]
# Global_Cell[Global_Cell$AI==0,"AI"]<-NA
# Global_Cell <- filter(Global_Cell,!is.na(AI))
summary(Global_Cell)
write.csv(Global_Cell,"~/Desktop/phD/AFEC-X/GrassGang/data/Global_Cell.csv",row.names=F)
grassgrid <- rasterFromXYZ(Global_Cell[,c("x","y","ID")])


GrassDistri <- grassdistri@data %>% count(Species)
# dir.create("~/Desktop/phD/AFEC-X/GrassGang/data/GrassDistri")
pb <- txtProgressBar(min=1,max=nrow(GrassDistri))
for(i in 1:nrow(GrassDistri)){
  setTxtProgressBar(pb,i)
  grassco<-matrix(grassdistri@coords[grassdistri@data$Species==GrassDistri$Species[i],],ncol=2)
  grasstmp <- extract(grassgrid,grassco)
  write.csv(grasstmp,paste0("~/Desktop/phD/AFEC-X/GrassGang/data/GrassDistri/",GrassDistri$Species[i],".csv"),row.names = F)
}
close(pb)
GrassDistri$sp.file <- paste0("~/Desktop/phD/AFEC-X/GrassGang/data/GrassDistri/",GrassDistri$Species,".csv")


```

Now see the geographic relationship between aridity  index and NDF
```{r}
Global_Cell <- read.csv("~/Desktop/phD/AFEC-X/GrassGang/data/Global_Cell.csv")
grassdistri <- fread("~/Desktop/phD/AFEC-X/GrassGang/data/BIEN_poaceae.csv")
library(rgdal)
library(raster)
coordinates(grassdistri)<-c("longmid","latmid")
proj4string(grassdistri) <- CRS('+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs')
GrassDistri <- grassdistri@data %>% count(Species)
GrassDistri$sp.file <- paste0("~/Desktop/phD/AFEC-X/GrassGang/data/GrassDistri/",GrassDistri$Species,".csv")

head(cell_append)
dim(cell_append)


# See C4 plants first
cellulose2 <- cell_append %>% filter(Pathway=="C4")
Global_Cell$cell.count<-0
Global_Cell$NDF.sum<-0

pb <- txtProgressBar(min=0,max=nrow(cellulose2))
for(i in 1:nrow(cellulose2)){
  setTxtProgressBar(pb,i)
  tmp <- fread(GrassDistri[GrassDistri$Species==cellulose2$Species[i],"sp.file"])
  Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"]+1
  Global_Cell[Global_Cell$ID%in%tmp$x,"NDF.sum"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"NDF.sum"]+cellulose2$NDF[i]
}
close(pb)


Global_Cell$NDF.mean <- Global_Cell$NDF.sum/Global_Cell$cell.count
library(raster)
plot(rasterFromXYZ(Global_Cell[,c("x","y","NDF.mean")]))

Glo.cell <- Global_Cell[Global_Cell$cell.count>0,]

summary(Glo.cell$cell.count)
Glo.cell$AI.sqrt <- sqrt(Glo.cell$AI)
Glo.cell$NDF.log <- log(Glo.cell$NDF.mean)
ggplot(Glo.cell,aes(x=AI.sqrt,y=NDF.log))+geom_point()+geom_smooth(method="lm")


summary(lm(NDF.log~AI.sqrt,data=Glo.cell))



#C3 then
cellulose2 <- cell_append %>% filter(Pathway=="C3")
Global_Cell$cell.count<-0
Global_Cell$NDF.sum<-0

pb <- txtProgressBar(min=0,max=nrow(cellulose2))
for(i in 1:nrow(cellulose2)){
  setTxtProgressBar(pb,i)
  tmp <- fread(GrassDistri[GrassDistri$Species==cellulose2$Species[i],"sp.file"])
  Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"]+1
  Global_Cell[Global_Cell$ID%in%tmp$x,"NDF.sum"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"NDF.sum"]+cellulose2$NDF[i]
}
close(pb)


Global_Cell$NDF.mean <- Global_Cell$NDF.sum/Global_Cell$cell.count

plot(rasterFromXYZ(Global_Cell[,c("x","y","NDF.mean")]))

Glo.cell <- Global_Cell[Global_Cell$cell.count>0,]

summary(Glo.cell$cell.count)
Glo.cell$AI.sqrt <- sqrt(Glo.cell$AI)
Glo.cell$NDF.log <- log(Glo.cell$NDF.mean)
ggplot(Glo.cell,aes(x=AI.sqrt,y=NDF.log))+geom_point()+geom_smooth(method="lm")


summary(lm(NDF.log~AI.sqrt,data=Glo.cell))

```
Next I want to see the relationship between aridity index and Cellulose
```{r}
# C4 first
cellulose2 <- cell_append %>% filter(Pathway=="C4"&!is.na(Cellulose))
Global_Cell$cell.count<-0
Global_Cell$Cellulose.sum<-0

pb <- txtProgressBar(min=0,max=nrow(cellulose2))
for(i in 1:nrow(cellulose2)){
  setTxtProgressBar(pb,i)
  tmp <- fread(GrassDistri[GrassDistri$Species==cellulose2$Species[i],"sp.file"])
  Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"]+1
  Global_Cell[Global_Cell$ID%in%tmp$x,"Cellulose.sum"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"Cellulose.sum"]+cellulose2$Cellulose[i]
}
close(pb)


Global_Cell$Cellulose.mean <- Global_Cell$Cellulose.sum/Global_Cell$cell.count

plot(rasterFromXYZ(Global_Cell[,c("x","y","Cellulose.mean")]))

Glo.cell <- Global_Cell[Global_Cell$cell.count>0,]

summary(Glo.cell$cell.count)
Glo.cell$AI.sqrt <- sqrt(Glo.cell$AI)
Glo.cell$Cellulose.log <- log(Glo.cell$Cellulose.mean)
ggplot(Glo.cell,aes(x=AI.sqrt,y=Cellulose.log))+geom_point()+geom_smooth(method="lm")


summary(lm(Cellulose.log~AI.sqrt,data=Glo.cell))

# C3 then
cellulose2 <- cell_append %>% filter(Pathway=="C3"&!is.na(Cellulose))
Global_Cell$cell.count<-0
Global_Cell$Cellulose.sum<-0

pb <- txtProgressBar(min=0,max=nrow(cellulose2))
for(i in 1:nrow(cellulose2)){
  setTxtProgressBar(pb,i)
  tmp <- fread(GrassDistri[GrassDistri$Species==cellulose2$Species[i],"sp.file"])
  Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"]+1
  Global_Cell[Global_Cell$ID%in%tmp$x,"Cellulose.sum"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"Cellulose.sum"]+cellulose2$Cellulose[i]
}
close(pb)


Global_Cell$Cellulose.mean <- Global_Cell$Cellulose.sum/Global_Cell$cell.count

plot(rasterFromXYZ(Global_Cell[,c("x","y","Cellulose.mean")]))

Glo.cell <- Global_Cell[Global_Cell$cell.count>0,]

summary(Glo.cell$cell.count)
Glo.cell$AI.sqrt <- sqrt(Glo.cell$AI)
Glo.cell$Cellulose.log <- log(Glo.cell$Cellulose.mean)
ggplot(Glo.cell,aes(x=AI.sqrt,y=Cellulose.log))+geom_point()+geom_smooth(method="lm")


summary(lm(Cellulose.log~AI.sqrt,data=Glo.cell))
```



##Plot generating for final presentation
```{r}
NDFplotC34<-cell_append%>%filter(!is.na(Pathway)&Pathway!="both")%>%mutate(Photosynthetic.types=Pathway)%>%ggplot()+aes(x=arid.sqrt,y=NDF,colour=Photosynthetic.types)+geom_point(alpha=0.3)+geom_smooth(method="lm")+xlab("")+ylab("NDF")+theme_classic()
CellplotC34<-cell_append%>%filter(!is.na(Pathway)&Pathway!="both")%>%mutate(Photosynthetic.types=Pathway)%>%ggplot()+aes(x=arid.sqrt,y=log.Cellulose,colour=Photosynthetic.types)+geom_point(alpha=0.3)+geom_smooth(method="lm")+xlab("")+ylab("Cellulose (log)")+theme_classic()
NDFplot<-cell_append%>%ggplot()+aes(x=arid.sqrt,y=NDF)+geom_point(size=1,alpha=0.5)+geom_smooth(method="lm")+xlab("")+ylab("NDF")+theme_classic()

Cellplot<-cell_append%>%ggplot()+aes(x=arid.sqrt,y=log.Cellulose)+geom_point()+geom_smooth(method="lm")+ylab("Cellulose (log)")+theme_classic()+xlab("Aridity Index")
summary(lm(log.Cellulose~arid.sqrt, data=cell_append))


LAnewdata <- data.frame(arid.sqrt=seq(0,1.5,0.01))
LAlm<-lm(logLArea~arid.sqrt, data=grasstrait)
LApred<-predict(LAlm,LAnewdata,se.fit=T)
LAnewdata$log.upw<-LApred$fit+1.96*LApred$se.fit
LAnewdata$log.low<-LApred$fit-1.96*LApred$se.fit
LAnewdata$pred <- exp(LApred$fit)
LAnewdata$up<-exp(LAnewdata$log.upw)
LAnewdata$lo<-exp(LAnewdata$log.low)
LAplot<-grasstrait%>%mutate(LA=exp(logLArea))%>%ggplot()+aes(x=arid.sqrt,y=LA)+geom_point()+geom_smooth(data=LAnewdata,aes(x=arid.sqrt,y=pred,ymin=lo,ymax=up),stat="identity")+theme_classic()+xlab("Aridity Index")+ylab("Leaf Area")+ylim(0,35)


LAplotC34<-ggplot(grasstrait[!is.na(grasstrait$Photosynthetic.types)&grasstrait$Photosynthetic.types!="both",],aes(x=arid.sqrt,y=logLArea,color=Photosynthetic.types))+geom_point(alpha=0.3)+geom_smooth(method="lm")+theme_classic()+xlab("")+ylab("Leaf Area (log)")
grasstrait2<-grasstrait[!is.na(grasstrait$Photosynthetic.types)&grasstrait$Photosynthetic.types!="both",]
summary(lm(logLArea~arid.sqrt*Photosynthetic.types, data=grasstrait2))
summary(lm(logLArea~arid.sqrt, data=grasstrait))

thickplot<-thick %>% filter(count>=10&!is.na(thick.log))%>%ggplot()+aes(x=arid.sqrt,y=thick.log)+geom_point(size=1,alpha=0.5)+geom_smooth(method="lm")+theme_classic()+xlab("")+ylab("Thickness (log)")
thickplotC34<-thick %>% filter(count>=10&!is.na(thick.log),Photosynthetic.types!="both"&!is.na(Photosynthetic.types))%>%ggplot()+aes(x=arid.sqrt,y=thick.log,color=Photosynthetic.types)+geom_point(alpha=0.3)+geom_smooth(method="lm")+theme_classic()+xlab("")+ylab("Thickness (log)")
summary(lm(thick.log~arid.sqrt,data=thick))
summary(lm(thick.log~arid.sqrt*Photosynthetic.types, data=thick[thick$count>=10&!is.na(thick$thick.log)&thick$Photosynthetic.types!="both"&!is.na(thick$Photosynthetic.types),]))

coltgh_append2 <- data.frame(accepted_name=c(coltgh_agg$Binomial,leaftgh$accepted_name),arid.sqrt=c(coltgh_agg$arid.sqrt,leaftgh$arid.sqrt),Toughness=c(coltgh_agg$Mean,leaftgh$Value))

coltgh_append2$log.tough <- log(coltgh_append2$Toughness)

toughplot<-coltgh_append2 %>% filter(Toughness<=11)%>% ggplot()+aes(x=arid.sqrt,y=log.tough)+geom_point(size=1,alpha=0.5)+geom_smooth(method="lm")+theme_classic()+xlab("")+ylab("Toughness (log)")

toughplotC34<-coltgh_append %>% filter(Toughness<=11)%>% ggplot()+aes(x=arid.sqrt,y=log.tough,color=Photosynthetic.types)+geom_point(alpha=0.3)+geom_smooth(method="lm")+theme_classic()+xlab("")+ylab("Toughness (log)")

summary(lm(log.tough~arid.sqrt*Photosynthetic.types,data=coltgh_append))
summary(lm(log.tough~arid.sqrt,data=coltgh_append2))

toughplot2<-coltgh_agg %>% filter(log.tough<=2.4&log.tough>=0.8)%>%ggplot()+aes(x=arid.sqrt,y=log.tough)+geom_point()+geom_smooth(method="lm")+theme_classic()+ylab("Toughness (log)")+xlab("Aridity Index")

summary(lm(log.tough~arid.sqrt,data=coltgh_agg[coltgh_agg$log.tough<=2.4&coltgh_agg$log.tough>=0.8,]))

library(patchwork)
LAplot+toughplot2+Cellplot
ggsave("~/Desktop/phD/AFEC-X/GrassGang/Figures/Hypo1.pdf",width=8,height=4,dpi=600,units="in")

LAplotC34+thickplotC34+toughplotC34+NDFplotC34+CellplotC34+guide_area()+plot_layout(ncol=3,nrow=2,guides = "collect")
ggsave("~/Desktop/phD/AFEC-X/GrassGang/Figures/Hypo2.pdf",width=8,height=4,dpi=600,units="in")


LAplot
ggsave("~/Desktop/phD/AFEC-X/GrassGang/Figures/Hypo1LAplot.pdf",width=4.5,height=3,dpi=600,units="in")
Cellplot
ggsave("~/Desktop/phD/AFEC-X/GrassGang/Figures/Hypo1Cellplot.pdf",width=4.5,height=3,dpi=600,units="in")
toughplot2
ggsave("~/Desktop/phD/AFEC-X/GrassGang/Figures/Hypo1Toughplot.pdf",width=4.5,height=3,dpi=600,units="in")

```

##AusTraits
Still cannot find the traits we need...
```{r, eval=FALSE}
remotes::install_github("traitecoevo/austraits", 
                        dependencies = TRUE, upgrade = "ask", 
                        build_vignettes = TRUE)

vignette("austraits")
library(austraits)
austraits <- load_austraits(version = "3.0.2", path = "data/austraits")
summarise_austraits(austraits, "trait_name")$trait_name
```

