---
title: "Grass"
author: "WangJY"
date: "2022-11-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message=FALSE)
rm(list=ls())
gc()
# setwd("~/Desktop/phD/AFEC-X/GrassGang")
```

## C3/C4 matching
```{r}
library(readxl)
library(stringr)
library(tidyverse)
genuslevel <- read_xls("~/Desktop/phD/AFEC-X/GrassGang/data/genus-level.xls",sheet=1)[-c(1:6),]
colnames(genuslevel) <- genuslevel[1,]
genuslevel <- genuslevel[-1,]
genuslevel$genus <- str_split_fixed(genuslevel$`Genus Authority`,pattern=" ",n=2)[,1]
genuslevel <- genuslevel[,c("genus","Photosynthetic types")]

specieslevel <- read_xls("~/Desktop/phD/AFEC-X/GrassGang/data/species-level.xls",sheet=1)[-c(1:2),]
colnames(specieslevel) <- specieslevel[1,]
specieslevel <- specieslevel[-1,]
specieslevel <- specieslevel[,c("Species","Pathway")]
```

Now I have cleaned up dataset for C3 and C4 plant list, on genus level and species level. See below:
```{r}
head(genuslevel)
head(specieslevel)
```

```{r}
arid <- read.csv("~/Desktop/phD/AFEC-X/GrassGang/data/poaceae_mean_aridity.csv")
any(specieslevel$Species %in% arid$Species)

unique(genuslevel$`Photosynthetic types`)
genuslevel$`Photosynthetic types`[genuslevel$`Photosynthetic types`!="C3"&genuslevel$`Photosynthetic types`!="C4"&genuslevel$`Photosynthetic types`!="unknown"] <- "both"

unique(specieslevel$Pathway)
specieslevel$Pathway[specieslevel$Pathway=="C3-C4?"]<- "both"


head(arid)

GrassDataset<-arid %>% mutate(Species_old=Species,aridity.ch,count=x1,authors_WCVP,rank,accepted_name,accepted_authors,accepted_genus,accepted_family,accepted_order) %>%
  filter(!is.na(aridity.ch)) %>%
  dplyr::select(Species_old,aridity.ch,count,authors_WCVP,rank,accepted_name,accepted_authors,accepted_genus,accepted_family,accepted_order)
summary(GrassDataset$aridity.ch)

colnames(genuslevel)[1] <- c("accepted_genus")
GrassDataset <- left_join(GrassDataset,genuslevel)
unique(GrassDataset$`Photosynthetic types`)

colnames(specieslevel)[1] <- "Species_old"
GrassDataset <- left_join(GrassDataset,specieslevel)
GrassDataset[!is.na(GrassDataset$Pathway),"Photosynthetic types"] <- GrassDataset[!is.na(GrassDataset$Pathway),"Pathway"]
GrassDataset <- GrassDataset[,c(1:11)]
# write.csv(GrassDataset,"data/GrassDataset.csv",row.names=F)
```

Now I have complete dataset for Poaceae grass, with photosynthetic pathways.

## Cellulose against aridity index

```{r}
library(data.table)
library(openxlsx)
cellulose <- read_xlsx("~/Desktop/phD/AFEC-X/GrassGang/data/Lee2018_Article_AGlobalComparisonOfTheNutritiv SUPPLEMENTARY.xlsx",sheet=2)
cellulose <- cellulose[-c(1:4),1:12]
colnames(cellulose)<-cellulose[1,]
cellulose <- cellulose[-1,]

tmp <- GrassDataset[,c("Species_old","aridity.ch","accepted_name")]
colnames(tmp)[1:2] <- c("Species" ,"arid1")
cellulose <- left_join(cellulose,tmp[,c(1:2)])
tmp <- GrassDataset[,c("Species_old","aridity.ch","accepted_name")]
colnames(tmp)[2:3] <- c("arid2","Species" )
cellulose <- left_join(cellulose,tmp[,c(2:3)])

cellulose[is.na(cellulose$arid2)&!is.na(cellulose$arid1),"arid2"]<-cellulose[is.na(cellulose$arid2)&!is.na(cellulose$arid1),"arid1"]

cellulose <- cellulose[,c(1,7:12,14)]
summary(cellulose)
cellulose$ADF<- as.numeric(cellulose$ADF)
cellulose$ADL<- as.numeric(cellulose$ADL)
cellulose$Ash<- as.numeric(cellulose$Ash)
cellulose$CP<- as.numeric(cellulose$CP)
cellulose$DM<- as.numeric(cellulose$DM)
cellulose$NDF<- as.numeric(cellulose$NDF)

cellulose <- cellulose[!is.na(cellulose$NDF)&!is.na(cellulose$arid2),]
summary(cellulose)
cellulose$Species <- as.factor(cellulose$Species)
meanna <- function(vector){
  return(mean(vector,na.rm=T))
}
cell_agg <- aggregate(cellulose, by=list(cellulose$Species),FUN=mean)
cell_agg <- cell_agg[,-2]
colnames(cell_agg)[1]<- "Species"

tmp <- GrassDataset[,c("Species_old","Photosynthetic types","accepted_name")]
colnames(tmp)[1:2] <- c("Species","Pathway1")
cell_comp <- unique(left_join(cell_agg,tmp[1:2]))

tmp <- GrassDataset[,c("Species_old","Photosynthetic types","accepted_name")]
colnames(tmp)[2:3] <- c("Pathway2","Species")
cell_comp <- unique(left_join(cell_comp,tmp[2:3]))

#all same
cell_comp <- cell_comp[,-10]
hist(sqrt(cell_comp$arid2))
cell_comp$arid2.sqrt <- sqrt(cell_comp$arid2)
hist((cell_comp$NDF))





cell_supp<-read.xlsx("/Users/lilywang/Desktop/phD/AFEC-X/GrassGang/data/Grass cellulose.xlsx",sheet=1)
unique(cell_supp[,1])
cell_supp[cell_supp$Name=="Cenchrus ciliaris ",1]<-"Cenchrus ciliaris"
cell_supp[cell_supp$Name=="Cynodon dactylon ",1]<-"Cynodon dactylon"
cell_supp[cell_supp$Name=="Dichanthium annulatum ",1]<-"Dichanthium annulatum"
cell_supp[cell_supp$Name=="Panicum coloratum ",1]<-"Panicum coloratum"
cell_supp_agg<-aggregate(cell_supp,by=list(cell_supp$Name),FUN=meanna)
cell_supp_agg<-cell_supp_agg[,-2]
tmp <- GrassDataset[,c("Species_old","aridity.ch","accepted_name","count","Photosynthetic types")]
colnames(tmp)[1]<-"Group.1"
cell_supp_agg <- left_join(cell_supp_agg,tmp[,c(1,2,4,5)])
colnames(cell_supp_agg)[7]<- "Pathway1"

tmp <- GrassDataset[,c("Species_old","aridity.ch","accepted_name","count","Photosynthetic types")]
colnames(tmp)[3]<-"Group.1"
cell_supp_agg <- left_join(cell_supp_agg,tmp[,c(2,3,4,5)])

cell_supp_agg$arid.sqrt<-sqrt(cell_supp_agg$aridity.ch)
hist(cell_supp_agg$Cellulose)


cell_supp_agg%>%filter(!is.na(Pathway1))%>%ggplot()+aes(x=arid.sqrt,y=NDF,colour=Pathway1)+geom_point()+geom_smooth(method="lm")
cell_supp_agg%>%filter(!is.na(Pathway1))%>%ggplot()+aes(x=arid.sqrt,y=Cellulose,colour=Pathway1)+geom_point()+geom_smooth(method="lm")
cell_supp_agg%>%filter(!is.na(Pathway1))%>%ggplot()+aes(x=arid.sqrt,y=Hemicellulose,colour=Pathway1)+geom_point()+geom_smooth(method="lm")

 
  
cell_comp %>% filter(Pathway1=="C3"|Pathway1=="both")%>%ggplot()+aes(x=arid2.sqrt,y=NDF)+geom_point()+geom_smooth(method="lm")


cell_comp%>%filter(Pathway1!="both")%>%ggplot()+aes(x=arid2.sqrt,y=ADF-ADL,colour=Pathway1)+geom_point()+geom_smooth(method="lm")+ylab("Cellulose")




any(cell_supp_agg$Group.1%in%cell_comp[,"Species"])
cell_supp_agg<-unique(cell_supp_agg)

cell_new <- cell_supp_agg[!cell_supp_agg$Group.1%in%cell_comp[,"Species"],]
cell_exist <- cell_supp_agg[cell_supp_agg$Group.1%in%cell_comp[,"Species"],]

cell_append <- data.frame(Species=c(cell_comp$Species,cell_new$Group.1),NDF=c(cell_comp$NDF,cell_new$NDF),Cellulose=c(cell_comp$ADF-cell_comp$ADL,cell_new$Cellulose),Pathway=c(cell_comp$Pathway1,cell_new$Pathway1),arid.sqrt=c(cell_comp$arid2.sqrt,cell_new$arid.sqrt))

cell_append<-unique(cell_append)

cell_append[cell_append$Species%in%cell_exist$Group.1,"Cellulose"] <- cell_exist[,"Cellulose"]



cell_append%>%filter(!is.na(Pathway)&Pathway!="both")%>%ggplot()+aes(x=arid.sqrt,y=NDF,colour=Pathway)+geom_point()+geom_smooth(method="lm")
cell_append%>%filter(!is.na(Pathway)&Pathway!="both")%>%ggplot()+aes(x=arid.sqrt,y=Cellulose,colour=Pathway)+geom_point()+geom_smooth(method="lm")




cell_append2 <- cell_append[!is.na(cell_append$Pathway)&cell_append$Pathway!="both",]
cell_append2$Pathway <- as.factor(cell_append2$Pathway)
summary(lm(Cellulose~arid.sqrt*Pathway, data=cell_append2))


```


Not pattern we suggested, Now I will try leaf trait

#Leaf trait

```{r}
trait <- read.csv("/Users/lilywang/Desktop/phD/AFEC-X/GrassGang/data/TRY_traitdata_poales.csv")
head(trait)
colnames(trait)[1]<-"Species_old"

grasstrait <- left_join(GrassDataset,trait[,1:5])
head(grasstrait)

grasstrait$arid.sqrt <- sqrt(grasstrait$aridity.ch)
str(grasstrait)
head(grasstrait)
grasstrait <- grasstrait[grasstrait$count>=10,]
p1<-ggplot(grasstrait,aes(x=arid.sqrt,y=logSLA))+geom_point()+geom_smooth(method="lm");
p2<-ggplot(grasstrait,aes(x=arid.sqrt,y=LDMC))+geom_point()+geom_smooth(method="lm");
p3<-ggplot(grasstrait,aes(x=arid.sqrt,y=logLArea))+geom_point()+geom_smooth(method="lm");
p4<-ggplot(grasstrait,aes(x=arid.sqrt,y=leafN.sqrt))+geom_point()+geom_smooth(method="lm")
library(patchwork)
p1+p2+p3+p4
summary(lm(logLArea~arid.sqrt, data=grasstrait))
```

Now try leaf thickness

```{r}
library(data.table)
pth <- fread("/Users/lilywang/Desktop/phD/AFEC-X/GrassGang/data/leaf_thickness_w poaceae/23473.txt")
allth <- fread("/Users/lilywang/Desktop/phD/AFEC-X/GrassGang/data/leaf_thickness/23472.txt")
head(allth)

pthf<-allth %>% filter(AccSpeciesName%in%GrassDataset$accepted_name)
rm(allth)
gc()
head(pthf)
pthf <-pthf %>% filter(!is.na(TraitID))
# write.csv(pthf,"/Users/lilywang/Desktop/phD/AFEC-X/GrassGang/data/poaceae_leafthickness.csv",row.names=F)
# pthf <- read.csv("/Users/lilywang/Desktop/phD/AFEC-X/GrassGang/data/poaceae_leafthickness.csv")
head(pthf)
pthf <- pthf[,c("AccSpeciesName","StdValue")]
colnames(pthf)[1]<-"accepted_name"
pthf <- aggregate(pthf,by=list(pthf$accepted_name),FUN=meanna)
pthf <- pthf[,-2]
pthf  <- pthf %>% filter(!is.nan(StdValue))
colnames(pthf)[1]<-"accepted_name"
thick <- left_join(GrassDataset,pthf)
thick$arid.sqrt <- sqrt(thick$aridity.ch)
hist(log(thick$StdValue))
thick$thick.log <- log(thick$StdValue)
thick %>% filter(count>=10&!is.na(thick.log))%>%ggplot()+aes(x=arid.sqrt,y=thick.log)+geom_point()+geom_smooth(method="lm")

```

##Grass distribution data
```{r, eval=FALSE}
grassdistri <- fread("~/Desktop/phD/AFEC-X/GrassGang/data/BIEN_poaceae.csv")
head(grassdistri)
length(unique(grassdistri$Species))
plot(grassdistri[,c("longmid","latmid")])
summary((grassdistri %>% count(Species))$n)
library(rgdal)
coordinates(grassdistri)<-c("longmid","latmid")
proj4string(grassdistri) <- CRS('+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs')
mollweide <- "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84"

library(raster)
airas <- raster("~/Desktop/phD/AFEC-X/GrassGang/data/Aridity/ai_v3_yr.tif")
plot(airas)
crs(airas) #WGS1984
res(airas) # 0.0083333
airas_agg <- aggregate(airas, fact=60, fun=mean)
# writeRaster(airas_agg,"~/Desktop/phD/AFEC-X/GrassGang/data/Aridity/aridity_0.5deg.tif")
rm(airas)
gc()

res(airas_agg)
summary(values(airas_agg))
values(airas_agg) <- values(airas_agg)*0.0001
plot(airas_agg)
Global_Cell <- as.data.frame(rasterToPoints(airas_agg))
Global_Cell$ID=1:length(values(airas_agg))
Global_Cell$AI <- extract(airas_agg,Global_Cell[,c("x","y")],method="simple")

Global_Cell <- Global_Cell[,c("ID","x","y","AI")]
# Global_Cell[Global_Cell$AI==0,"AI"]<-NA
# Global_Cell <- filter(Global_Cell,!is.na(AI))
summary(Global_Cell)
write.csv(Global_Cell,"~/Desktop/phD/AFEC-X/GrassGang/data/Global_Cell.csv",row.names=F)
grassgrid <- rasterFromXYZ(Global_Cell[,c("x","y","ID")])


GrassDistri <- grassdistri@data %>% count(Species)
# dir.create("~/Desktop/phD/AFEC-X/GrassGang/data/GrassDistri")
pb <- txtProgressBar(min=1,max=nrow(GrassDistri))
for(i in 1:nrow(GrassDistri)){
  setTxtProgressBar(pb,i)
  grassco<-matrix(grassdistri@coords[grassdistri@data$Species==GrassDistri$Species[i],],ncol=2)
  grasstmp <- extract(grassgrid,grassco)
  write.csv(grasstmp,paste0("~/Desktop/phD/AFEC-X/GrassGang/data/GrassDistri/",GrassDistri$Species[i],".csv"),row.names = F)
}
close(pb)
GrassDistri$sp.file <- paste0("~/Desktop/phD/AFEC-X/GrassGang/data/GrassDistri/",GrassDistri$Species,".csv")


```

Now see the geographic relationship between aridity  index and NDF
```{r}
Global_Cell <- read.csv("~/Desktop/phD/AFEC-X/GrassGang/data/Global_Cell.csv")
grassdistri <- fread("~/Desktop/phD/AFEC-X/GrassGang/data/BIEN_poaceae.csv")
library(rgdal)
library(raster)
coordinates(grassdistri)<-c("longmid","latmid")
proj4string(grassdistri) <- CRS('+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs')
GrassDistri <- grassdistri@data %>% count(Species)
GrassDistri$sp.file <- paste0("~/Desktop/phD/AFEC-X/GrassGang/data/GrassDistri/",GrassDistri$Species,".csv")

head(cell_append)
dim(cell_append)


# See C4 plants first
cellulose2 <- cell_append %>% filter(Pathway=="C4")
Global_Cell$cell.count<-0
Global_Cell$NDF.sum<-0

pb <- txtProgressBar(min=0,max=nrow(cellulose2))
for(i in 1:nrow(cellulose2)){
  setTxtProgressBar(pb,i)
  tmp <- fread(GrassDistri[GrassDistri$Species==cellulose2$Species[i],"sp.file"])
  Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"]+1
  Global_Cell[Global_Cell$ID%in%tmp$x,"NDF.sum"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"NDF.sum"]+cellulose2$NDF[i]
}
close(pb)


Global_Cell$NDF.mean <- Global_Cell$NDF.sum/Global_Cell$cell.count
library(raster)
plot(rasterFromXYZ(Global_Cell[,c("x","y","NDF.mean")]))

Glo.cell <- Global_Cell[Global_Cell$cell.count>0,]

summary(Glo.cell$cell.count)
Glo.cell$AI.sqrt <- sqrt(Glo.cell$AI)
Glo.cell$NDF.log <- log(Glo.cell$NDF.mean)
ggplot(Glo.cell,aes(x=AI.sqrt,y=NDF.log))+geom_point()+geom_smooth(method="lm")


summary(lm(NDF.log~AI.sqrt,data=Glo.cell))



#C3 then
cellulose2 <- cell_append %>% filter(Pathway=="C3")
Global_Cell$cell.count<-0
Global_Cell$NDF.sum<-0

pb <- txtProgressBar(min=0,max=nrow(cellulose2))
for(i in 1:nrow(cellulose2)){
  setTxtProgressBar(pb,i)
  tmp <- fread(GrassDistri[GrassDistri$Species==cellulose2$Species[i],"sp.file"])
  Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"]+1
  Global_Cell[Global_Cell$ID%in%tmp$x,"NDF.sum"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"NDF.sum"]+cellulose2$NDF[i]
}
close(pb)


Global_Cell$NDF.mean <- Global_Cell$NDF.sum/Global_Cell$cell.count

plot(rasterFromXYZ(Global_Cell[,c("x","y","NDF.mean")]))

Glo.cell <- Global_Cell[Global_Cell$cell.count>0,]

summary(Glo.cell$cell.count)
Glo.cell$AI.sqrt <- sqrt(Glo.cell$AI)
Glo.cell$NDF.log <- log(Glo.cell$NDF.mean)
ggplot(Glo.cell,aes(x=AI.sqrt,y=NDF.log))+geom_point()+geom_smooth(method="lm")


summary(lm(NDF.log~AI.sqrt,data=Glo.cell))

```
Next I want to see the relationship between aridity index and Cellulose
```{r}
# C4 first
cellulose2 <- cell_append %>% filter(Pathway=="C4"&!is.na(Cellulose))
Global_Cell$cell.count<-0
Global_Cell$Cellulose.sum<-0

pb <- txtProgressBar(min=0,max=nrow(cellulose2))
for(i in 1:nrow(cellulose2)){
  setTxtProgressBar(pb,i)
  tmp <- fread(GrassDistri[GrassDistri$Species==cellulose2$Species[i],"sp.file"])
  Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"]+1
  Global_Cell[Global_Cell$ID%in%tmp$x,"Cellulose.sum"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"Cellulose.sum"]+cellulose2$Cellulose[i]
}
close(pb)


Global_Cell$Cellulose.mean <- Global_Cell$Cellulose.sum/Global_Cell$cell.count

plot(rasterFromXYZ(Global_Cell[,c("x","y","Cellulose.mean")]))

Glo.cell <- Global_Cell[Global_Cell$cell.count>0,]

summary(Glo.cell$cell.count)
Glo.cell$AI.sqrt <- sqrt(Glo.cell$AI)
Glo.cell$Cellulose.log <- log(Glo.cell$Cellulose.mean)
ggplot(Glo.cell,aes(x=AI.sqrt,y=Cellulose.log))+geom_point()+geom_smooth(method="lm")


summary(lm(Cellulose.log~AI.sqrt,data=Glo.cell))

# C3 then
cellulose2 <- cell_append %>% filter(Pathway=="C3"&!is.na(Cellulose))
Global_Cell$cell.count<-0
Global_Cell$Cellulose.sum<-0

pb <- txtProgressBar(min=0,max=nrow(cellulose2))
for(i in 1:nrow(cellulose2)){
  setTxtProgressBar(pb,i)
  tmp <- fread(GrassDistri[GrassDistri$Species==cellulose2$Species[i],"sp.file"])
  Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"cell.count"]+1
  Global_Cell[Global_Cell$ID%in%tmp$x,"Cellulose.sum"] <-Global_Cell[Global_Cell$ID%in%tmp$x,"Cellulose.sum"]+cellulose2$Cellulose[i]
}
close(pb)


Global_Cell$Cellulose.mean <- Global_Cell$Cellulose.sum/Global_Cell$cell.count

plot(rasterFromXYZ(Global_Cell[,c("x","y","Cellulose.mean")]))

Glo.cell <- Global_Cell[Global_Cell$cell.count>0,]

summary(Glo.cell$cell.count)
Glo.cell$AI.sqrt <- sqrt(Glo.cell$AI)
Glo.cell$Cellulose.log <- log(Glo.cell$Cellulose.mean)
ggplot(Glo.cell,aes(x=AI.sqrt,y=Cellulose.log))+geom_point()+geom_smooth(method="lm")


summary(lm(Cellulose.log~AI.sqrt,data=Glo.cell))
```

##AusTraits
Still cannot find the traits we need...
```{r, eval=FALSE}
remotes::install_github("traitecoevo/austraits", 
                        dependencies = TRUE, upgrade = "ask", 
                        build_vignettes = TRUE)

vignette("austraits")
library(austraits)
austraits <- load_austraits(version = "3.0.2", path = "data/austraits")
summarise_austraits(austraits, "trait_name")$trait_name
```

