---
title: "Skull-Diet"
author: "WangJY"
date: "2022-11-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message=FALSE)
library(readxl)
library(openxlsx)
library(tidyverse)

library(arm)
library(car)
library(ggplot2)
library(ggrepel) #NEW LIBRARY!!
library(lme4) 
library(ape)
library(multcomp)
library(nlme)
library(visreg)
library(coefplot)
library(jtools)
library(Matrix)
library(lmerTest)
library(MuMIn)
library(multcomp)
require(graphics)
```

## Diet matrix
Diet data is collected from published articles, reference within table.

```{r Data processing from excel}
#specify file location
diet.data <- "/Users/lilywang/Desktop/phD/AFEC-X/Skull/Grass Gang/20221118_Herbivore_Diet_Database Grazers.xlsx"

excel_sheets(path = diet.data)

#extract diet data matrix
diet <- read_excel(diet.data, "Diet matrix",skip=5, col_types = c(rep("text",13),rep("numeric",12),rep("text",5),rep("numeric",33),rep("text",5)))

diet <- data.frame(diet)

head(diet)
diet$Binomial.name <- as.factor(diet$Binomial.name)
diet$Study<-as.factor(diet$Study)
diet$Output.Binomial.name <- as.factor(diet$Output.Binomial.name)
diet$Order <- as.factor(diet$Order)
diet$Family <- as.factor(diet$Family)

head(diet)
summary(diet)
dim(diet)
#reduce to columns of species for which we have data
diet <- diet[,colSums(is.na(diet))<nrow(diet)]
summary(diet)
dim(diet)
#check for inconsistencies in trait allocation  for plant species
dietplants <- diet[,c("Output.Binomial.name","Family","Order","Graminoid","Monocot","Woody","Spines")]
dietplants $x1 <- c(rep(1,each = (dim(dietplants)[1])))
namelist <- aggregate(x1~Output.Binomial.name+Graminoid+Monocot+Woody+Spines+Family+Order,dietplants,FUN=sum,na.action=na.omit) # calculate how many obs per plant
dim(namelist)
head(namelist)
summary(namelist$Output.Binomial.name)

#most spp should only have 1 record, except for species where leaves and fruits have been eaten
summary(namelist)

#check individual species
diet.spp <- subset(diet,!is.na(Alcelaphus_buselaphus))
dim(diet.spp)
#reduce to columns of species for which we have data
diet.spp <- diet.spp[,colSums(is.na(diet.spp))<nrow(diet.spp)]
summary(diet.spp)
diet.spp$Binomial.name <- as.factor(diet.spp$Binomial.name)
diet.spp <- diet.spp[order(-diet.spp$Spines), ]
head(diet.spp,n=10)
```

Now I have cleaned up the diet spreadsheet. Next I will calculate diet proportion for each species in each study-season combination.
```{r calculate proportional diet sums}
#now lets average per study per season first
#Why? because its very imbalanced to use multiple seasons for 1 study and 1 season for 1 study

head(diet,n=10)
dim(diet)
diet$study.season <- as.factor(paste(diet$Study,diet$Season))
head(diet$study.season,n=50)

str(diet$study.season)
study.season.list <- unique(diet$study.season)
length(study.season.list)


#NOTE the following loop is critical.
#it gets diet proportions AND  it gets community weighted mean traits in diets of each herbivore species in each season measured

diets.out <-NULL

for(i in 1:length(study.season.list)){
  print(i)
  df1 <- subset(diet,study.season==study.season.list[i])
  #df1 <- subset(diet,study.season=="132.Winter")
  dim(df1)
  
  # calculate sum of diet
  #WATCH OUT! the position of the first column may change!!
  diet1stcol <- which(colnames(df1)=="Site")+1
  dietlastcol <- which(colnames(df1)=="Study2")-1
  diet.sum.df <- data.frame(colSums(df1[,c(diet1stcol:dietlastcol)],na.rm=T))
  names(diet.sum.df) <- "sum"
  #diet.sum.df
  
  # calculate graminoid proportions
  gram.df <- subset(df1,Graminoid==1)
  diet.graminoid.df <- data.frame(colSums(gram.df[,c(diet1stcol:dietlastcol)],na.rm=T))
  names(diet.graminoid.df) <- "graminoid"
  #diet.graminoid.df
  
  # calculate monocot proportions
  monocot.df <- subset(df1,Monocot==1)
  diet.monocot.df <- data.frame(colSums(monocot.df[,c(diet1stcol:dietlastcol)],na.rm=T))
  names(diet.monocot.df) <- "monocot"
  #diet.monocot.df
  
  # calculate spiny plant proportions
  spiny.df <- subset(df1,Spines==1)
  diet.spine.df <- data.frame(colSums(spiny.df[,c(diet1stcol:dietlastcol)],na.rm=T))
  names(diet.spine.df) <- "spines"
  #diet.spine.df
  
  # calculate woody plant proportions
  woody.df <- subset(df1,Woody==1)
  diet.woody.df <- data.frame(colSums(woody.df[,c(diet1stcol:dietlastcol)],na.rm=T))
  names(diet.woody.df) <- "woody"
  
  
  # calculate forb plant proportions
  forb.df <- subset(df1,Forb==1)
  diet.forb.df <- data.frame(colSums(forb.df[,c(diet1stcol:dietlastcol)],na.rm=T))
  names(diet.forb.df) <- "forb"
  
  #calculate herb component as sum of monocots and forbs
  diet.herb.df <- diet.monocot.df + diet.forb.df
  names(diet.herb.df) <- "herb"
  
  # calculate fruit&flower plant proportions
  fruit.df <- subset(df1,Fruit.Flowers==1)
  diet.fruit.df <- data.frame(colSums(fruit.df[,c(diet1stcol:dietlastcol)],na.rm=T))
  names(diet.fruit.df) <- "fruit"
  
  # calculate bryophyte,Lich.Fungi proportions
  BLF.df <- subset(df1,Bryo.Lich.Fungi==1)
  diet.BLF.df <- data.frame(colSums(BLF.df[,c(diet1stcol:dietlastcol)],na.rm=T))
  names(diet.BLF.df) <- "BLF"
  
  # calculate unknown diet proportions
  unknown.df <- subset(df1,Unknown==1)
  diet.unknown.df <- data.frame(colSums(unknown.df[,c(diet1stcol:dietlastcol)],na.rm=T))
  names(diet.unknown.df) <- "unknown"
  
  #check total sum for food components
  diet.total.df <- diet.monocot.df + diet.woody.df  + diet.forb.df + diet.fruit.df + diet.BLF.df + diet.unknown.df
  names(diet.total.df) <- "total"
  
  
  #calculate average log leaf area
  LA.df <- subset(df1,!is.na(logLArea))
  #total sum
  diet.df1.tot <- data.frame(colSums(df1[,c(diet1stcol:dietlastcol)],na.rm=T))
  #need to multiply onto proportions
  diet.LA.tot <- data.frame(colSums(LA.df[,c(diet1stcol:dietlastcol)],na.rm=T))
  ratio = max(diet.df1.tot)/max(diet.LA.tot)
  #need to multiply onto proportions
  LA.df2 <- LA.df
  dim(LA.df);dim(LA.df2)
  LA.df2[,c(diet1stcol:dietlastcol)] <- LA.df[,c(diet1stcol:dietlastcol)]*LA.df$logLArea*ratio  #was 31?
  diet.LA.df <- data.frame(colSums(LA.df2[,c(diet1stcol:dietlastcol)],na.rm=T))
  names(diet.LA.df) <- "logLArea"
  
 
  #calculate average log SLA
  SLA.df <- subset(df1,!is.na(logSLA))
  #total sum
  diet.df1.tot <- data.frame(colSums(df1[,c(diet1stcol:dietlastcol)],na.rm=T))
  #need to multiply onto proportions
  diet.SLA.tot <- data.frame(colSums(SLA.df[,c(diet1stcol:dietlastcol)],na.rm=T))
  ratio = max(diet.df1.tot)/max(diet.SLA.tot)
  #need to multiply onto proportions
  SLA.df2 <- SLA.df
  SLA.df2[,c(diet1stcol:dietlastcol)] <- SLA.df[,c(diet1stcol:dietlastcol)]*SLA.df$logSLA*ratio  #was 31?
  diet.SLA.df <- data.frame(colSums(SLA.df2[,c(diet1stcol:dietlastcol)],na.rm=T))
  names(diet.SLA.df) <- "logSLA"
  
  
  #calculate average LDMC
  LDMC.df <- subset(df1,!is.na(LDMC))
  #total sum
  diet.df1.tot <- data.frame(colSums(df1[,c(diet1stcol:dietlastcol)],na.rm=T))
  #need to multiply onto proportions
  diet.LDMC.tot <- data.frame(colSums(LDMC.df[,c(diet1stcol:dietlastcol)],na.rm=T))
  ratio = max(diet.df1.tot)/max(diet.LDMC.tot)
  #need to multiply onto proportions
  LDMC.df2 <- LDMC.df
  LDMC.df2[,c(diet1stcol:dietlastcol)] <- LDMC.df[,c(diet1stcol:dietlastcol)]*LDMC.df$LDMC*ratio  #was 31?
  diet.LDMC.df <- data.frame(colSums(LDMC.df2[,c(diet1stcol:dietlastcol)],na.rm=T))
  names(diet.LDMC.df) <- "LDMC"
  
  
  #calculate average log leaf nitrogen
  LN.df <- subset(df1,!is.na(leafN.sqrt))
  #total sum
  diet.df1.tot <- data.frame(colSums(df1[,c(diet1stcol:dietlastcol)],na.rm=T))
  #need to multiply onto proportions
  diet.LN.tot <- data.frame(colSums(LN.df[,c(diet1stcol:dietlastcol)],na.rm=T))
  ratio = max(diet.df1.tot)/max(diet.LN.tot)
  #need to multiply onto proportions
  LN.df2 <- LN.df
  LN.df2[,c(diet1stcol:dietlastcol)] <- LN.df[,c(diet1stcol:dietlastcol)]*LN.df$leafN.sqrt*ratio  #was 31?
  diet.LN.df <- data.frame(colSums(LN.df2[,c(diet1stcol:dietlastcol)],na.rm=T))
  names(diet.LN.df) <- "leafN.sqrt"
  
  
  
  #combine together
  #diets.df <- cbind(diet.sum.df,diet.graminoid.df,diet.monocot.df,diet.spine.df,diet.woody.df)
  diets.df <- cbind(diet.sum.df,diet.graminoid.df,diet.monocot.df,diet.spine.df,diet.woody.df,diet.forb.df,diet.herb.df,diet.fruit.df,diet.BLF.df,diet.unknown.df,diet.total.df,diet.LA.df,diet.SLA.df,diet.LDMC.df,diet.LN.df)
  diets.df <- subset(diets.df,sum>0)
  
  
  #add in column with study name
  diets.df$Study <- factor(c(rep(df1$Study[1],each = (dim(diets.df)[1])))) 
  #add in column with season name
  diets.df$Season <- factor(c(rep(df1$Season[1],each = (dim(diets.df)[1])))) 
  #add in column with species name
  diets.df$Species <- row.names(diets.df)
  
  if(i==1) diets.out <- diets.df
  if(i>1) diets.out <- rbind(diets.out,diets.df)
  
}

summary(diets.out)
dim(diets.out)

diets.out$Species<- as.factor(diets.out$Species)

summary(diets.out$Species)

subset(diets.out,sum<0.95) #this command checks for sums < 1
subset(diets.out,sum>1.1) #this command checks for sums > 1
#usually this means more than one area sampled
#problem with fractions in study 21B (>1)
#study 146 may consist of multiple sites

subset(diets.out,Species=="Bubalus_arnee")

dim(diets.out)
```

Now I have the diet data for each species in each study in each season, so I'll take the average for each study.

```{r diet average per study}
#now we have the data per species per study per season
#this is where you can choose useful subsets e.g. average per species across studies, average per species across studies in 

#so lets average per study

diets <- cbind(aggregate(sum~Study+Species,diets.out,FUN=mean),aggregate(graminoid~Study+Species,diets.out,FUN=mean)[3],aggregate(monocot~Study+Species,diets.out,FUN=mean)[3],aggregate(spines~Study+Species,diets.out,FUN=mean)[3],aggregate(woody~Study+Species,diets.out,FUN=mean)[3],aggregate(forb~Study+Species,diets.out,FUN=mean)[3],aggregate(herb~Study+Species,diets.out,FUN=mean)[3],aggregate(fruit~Study+Species,diets.out,FUN=mean)[3],aggregate(BLF~Study+Species,diets.out,FUN=mean)[3],aggregate(unknown~Study+Species,diets.out,FUN=mean)[3],aggregate(total~Study+Species,diets.out,FUN=mean)[3],aggregate(logLArea~Study+Species,diets.out,FUN=mean)[3],aggregate(logSLA~Study+Species,diets.out,FUN=mean)[3],aggregate(LDMC~Study+Species,diets.out,FUN=mean)[3],aggregate(leafN.sqrt~Study+Species,diets.out,FUN=mean)[3])

dim(diets)
head(diets)

#you should print out this table and check it, to make sure you have no data problems with data input
# write_csv(diets,"/Users/lilywang/Desktop/phD/AFEC-X/Skull/Grass Gang/Herbivore_sums_check.csv")


summary(diets)
#now to get diet averages..
diets.ave <- aggregate (cbind(sum,graminoid,monocot,spines,woody,forb,herb,fruit,BLF,unknown,total)~Species,diets,FUN=mean)



#now average across studies to get a values per species

diets <- cbind(aggregate(sum~Species,diets,FUN=mean),aggregate(graminoid~Species,diets,FUN=mean)[2],aggregate(monocot~Species,diets,FUN=mean)[2],aggregate(spines~Species,diets,FUN=mean)[2],aggregate(woody~Species,diets,FUN=mean)[2],aggregate(herb~Species,diets,FUN=mean)[2],aggregate(logLArea~Species,diets,FUN=mean)[2],aggregate(logSLA~Species,diets,FUN=mean)[2],aggregate(LDMC~Species,diets,FUN=mean)[2],aggregate(leafN.sqrt~Species,diets,FUN=mean)[2])

dim(diets) #rows equal the number of species for which you have diet data


#calculate diet proportions

diets$graminoidP <- diets$graminoid/diets$sum
diets$monocotP <- diets$monocot/diets$sum
diets$spinyP <- diets$spines/diets$sum
diets$woodyP <- diets$woody/diets$sum
diets$herbP <- diets$herb/diets$sum


quartz()
par(mfrow=c(2,4))
hist(diets$graminoidP)
hist(diets$monocotP)
hist(diets$spinyP)
hist(diets$woodyP)
hist(diets$logLArea)
hist(diets$logSLA)  # SLA pretty skew??
hist(diets$LDMC)
hist(diets$leafN.sqrt)


diets$spinyP.log <- log(diets$spinyP+0.01)



```


## Relationship between diet and skull
Skull data was collected from skull specimen from museums worldwide. Aridity index was calculated based on its distribution.

```{r}
Skull<- read.csv("/Users/lilywang/Desktop/phD/AFEC-X/Skull/Grass Gang/skulldata_Grazer.csv",header=T)

summary(Skull)
dim(Skull)    


Skull$Species <- as.factor(Skull$Species)
Skull$Family <- as.factor(Skull$Family)
Skull$Subfamily <- as.factor(Skull$Subfamily)
Skull$Continent <- as.factor(Skull$Continent)
Skull$Diet <- as.factor(Skull$Diet)


#combine diet data with skull data

DF1 <- merge(diets, Skull,by = c("Species"),all.x=T)
summary(DF1)
dim(DF1)
head(DF1)

DF1$Species <- as.factor(DF1$Species)
length(unique(DF1$Species))

DF1$AI.sqrt <- sqrt(DF1$Aridity.Index)

skulldiet <- DF1
skulldiet$MZW.log<- log(skulldiet$MZW)
skulldiet$MASSETER.log <- log(skulldiet$MASSETER)
skulldiet$length.log<-log(skulldiet$SKULLLENGTH)

MZWlm1 <- lm(MZW.log~length.log+logLArea,data=skulldiet)
summary(MZWlm1)
quartz();par(mfrow=c(2,2));plot(MZWlm1)


MZWlm2 <- lm(MZW.log~length.log+logSLA,data=skulldiet)
summary(MZWlm2)
MZWlm3 <- lm(MZW.log~length.log+LDMC,data=skulldiet)
summary(MZWlm3)
MZWlm4 <- lm(MZW.log~length.log+leafN.sqrt,data=skulldiet)
summary(MZWlm4)

MSTlm1 <- lm(MASSETER.log~length.log+logLArea,data=skulldiet)
summary(MSTlm1)
MSTlm2 <- lm(MASSETER.log~length.log+logSLA,data=skulldiet)
summary(MSTlm2)
MSTlm3 <- lm(MASSETER.log~length.log+LDMC,data=skulldiet)
summary(MSTlm3)
MSTlm4 <- lm(MASSETER.log~length.log+leafN.sqrt,data=skulldiet)
summary(MSTlm4)

MZWlm1.1<-lm(MZW.log~length.log+logLArea,data=subset(skulldiet,Diet=="Grazer"))
summary(MZWlm1.1)
MZWlm2.1 <- lm(MZW.log~length.log+logSLA,data=subset(skulldiet,Diet=="Grazer"))
summary(MZWlm2.1)
MZWlm3.1 <- lm(MZW.log~length.log+LDMC,data=subset(skulldiet,Diet=="Grazer"))
summary(MZWlm3.1)
MZWlm4.1 <- lm(MZW.log~length.log+leafN.sqrt,data=subset(skulldiet,Diet=="Grazer"))
summary(MZWlm4.1)


MZWlm1.2<-lm(MZW.log~length.log+logLArea,data=subset(skulldiet,Dietdata=="Grazer"))
summary(MZWlm1.2)
MZWlm2.2 <- lm(MZW.log~length.log+logSLA,data=subset(skulldiet,Dietdata=="Grazer"))
summary(MZWlm2.2)
MZWlm3.2 <- lm(MZW.log~length.log+LDMC,data=subset(skulldiet,Dietdata=="Grazer"))
summary(MZWlm3.2)
MZWlm4.2 <- lm(MZW.log~length.log+leafN.sqrt,data=subset(skulldiet,Dietdata=="Grazer"))
summary(MZWlm4.2)



MSTlm1.1 <- lm(MASSETER.log~length.log+logLArea,data=subset(skulldiet,Diet=="Grazer"))
summary(MSTlm1.1)
MSTlm2.1 <- lm(MASSETER.log~length.log+logSLA,data=subset(skulldiet,Diet=="Grazer"))
summary(MSTlm2.1)
MSTlm3.1 <- lm(MASSETER.log~length.log+LDMC,data=subset(skulldiet,Diet=="Grazer"))
summary(MSTlm3.1)
MSTlm4.1 <- lm(MASSETER.log~length.log+leafN.sqrt,data=subset(skulldiet,Diet=="Grazer"))
summary(MSTlm4.1)


MSTlm1.2 <- lm(MASSETER.log~length.log+logLArea,data=subset(skulldiet,Dietdata=="Grazer"))
summary(MSTlm1.2)
MSTlm2.2 <- lm(MASSETER.log~length.log+logSLA,data=subset(skulldiet,Dietdata=="Grazer"))
summary(MSTlm2.2)
MSTlm3.2 <- lm(MASSETER.log~length.log+LDMC,data=subset(skulldiet,Dietdata=="Grazer"))
summary(MSTlm3.2)
MSTlm4.2 <- lm(MASSETER.log~length.log+leafN.sqrt,data=subset(skulldiet,Dietdata=="Grazer"))
summary(MSTlm4.2)



MZWlm1.3<-update(MZWlm1.1,.~.-length.log)
summary(MZWlm1.3)
MZWlm2.3<-update(MZWlm2.1,.~.-length.log)
summary(MZWlm2.3)
MZWlm3.3<-update(MZWlm3.1,.~.-length.log)
summary(MZWlm3.3)
MZWlm4.3<-update(MZWlm4.1,.~.-length.log)
summary(MZWlm4.3)

MZWlm1.4<-update(MZWlm1.2,.~.-length.log)
summary(MZWlm1.4)
MZWlm2.4<-update(MZWlm2.2,.~.-length.log)
summary(MZWlm2.4)
MZWlm3.4<-update(MZWlm3.2,.~.-length.log)
summary(MZWlm3.4)
MZWlm4.4<-update(MZWlm4.2,.~.-length.log)
summary(MZWlm4.4)


MSTlm1.3<-update(MSTlm1.1,.~.-length.log)
summary(MSTlm1.3)
MSTlm2.3<-update(MSTlm2.1,.~.-length.log)
summary(MSTlm2.3)
MSTlm3.3<-update(MSTlm3.1,.~.-length.log)
summary(MSTlm3.3)
MSTlm4.3<-update(MSTlm4.1,.~.-length.log)
summary(MSTlm4.3)

MSTlm1.4<-update(MSTlm1.2,.~.-length.log)
summary(MSTlm1.4)
MSTlm2.4<-update(MSTlm2.2,.~.-length.log)
summary(MSTlm2.4)
MSTlm3.4<-update(MSTlm3.2,.~.-length.log)
summary(MSTlm3.4)
MSTlm4.4<-update(MSTlm4.2,.~.-length.log)
summary(MSTlm4.4)





skp1<-ggplot(skulldiet,aes(x=logLArea,y=MZW.log))+geom_point()+geom_smooth(method="lm")+theme_classic();
skp2<-ggplot(skulldiet,aes(x=logSLA,y=MZW.log))+geom_point()+geom_smooth(method="lm")+theme_classic();
skp3<-ggplot(skulldiet,aes(x=LDMC,y=MZW.log))+geom_point()+geom_smooth(method="lm")+theme_classic();
skp4<-ggplot(skulldiet,aes(x=leafN.sqrt,y=MZW.log))+geom_point()+geom_smooth(method="lm")+theme_classic();
skp5<-ggplot(skulldiet,aes(x=logLArea,y=MASSETER.log))+geom_point()+geom_smooth(method="lm")+theme_classic();
skp6<-ggplot(skulldiet,aes(x=logSLA,y=MASSETER.log))+geom_point()+geom_smooth(method="lm")+theme_classic();
skp7<-ggplot(skulldiet,aes(x=LDMC,y=MASSETER.log))+geom_point()+geom_smooth(method="lm")+theme_classic();
skp8<-ggplot(skulldiet,aes(x=leafN.sqrt,y=MASSETER.log))+geom_point()+geom_smooth(method="lm")+theme_classic()

library(patchwork)
skp1+skp2+skp3+skp4+skp5+skp6+skp7+skp8+plot_layout(ncol=4,nrow=2)

```
